\textls[-0]{\thetitle}

### 2023-03-22 canonicitymodel.tex
resolve comments

  \denotesC{\goodType{\Gm}{\TyId{a}{b}}{}}(\gm)(\gm')(t) &= \{\star \ |  \text{ when } t \equiv \eqrefl{\sub{a}{\gm}} \text{ and } \sub{a}{\gm} \equiv \sub{b}{\gm} \} \YZ{What if the conditions do not hold? Empty set?}\EDJreply{Yes. It is a family of set indexed by t (or just a function maps t to a set), and if t is neither of the above, then the function will map to empty set.}\\

@@

The eccentric part of the proof-relevant logical-relations model is the
treatment of propositions.
The model treats proposition in a special way : \EDJ{Without this first sentence, this paragraph seems unmotivated.}\YZreply{Why is it 'difficult'? Is there a more appropriate adjective than 'difficult'?}\EDJreply{Don't you find difficult? At first sight, I cannot understand why this sentence, proposed by Sterling in two of his paper, can be valid mathematically. It only makes sense to me until I am in a type-theoretic world (by Kaposi, since Eq is an inductive type now) (or maybe topos-theoretically where categorical logic will encode equality using data like equalizer). What about changing the phrase to "eccentric" or "weird"?}
a proposition is encoded as a sub\-singleton. For
example, $\{\star^1 \ | \text{ when } t \equiv \true  \} \uplus \{\star^2 \
| \text{ when } t \equiv \false  \}$ represents a disjoint union of two
sub\-singleton sets, where the first one is either a singleton if we have a proof of
$t \equiv \true $ or an empty set otherwise.
In other words,
$\star^1$ witnesses a proof that $t \equiv \true$.
Here, $\star$, $\star^1$, $\star^2$ are just some arbitrary fixed elements.

>>>>

  \denotesC{\goodType{\Gm}{\TyId{a}{b}}{}}(\gm)(\gm')(t) &= \setc{\star}{\text{ when } t \equiv \eqrefl{\sub{a}{\gm}} \text{ and } \sub{a}{\gm} \equiv \sub{b}{\gm}} %\YZ{What if the conditions do not hold? Empty set?}\EDJreply{Yes. It is a family of set indexed by t (or just a function maps t to a set), and if t is neither of the above, then the function will map to empty set.}

@@

What is perhaps unintuitive about the proof-relevant logical-relations model is the
treatment of propositions.
%The model treats propositions in a special way : \EDJ{Without this first sentence, this paragraph seems unmotivated.}\YZreply{Why is it 'difficult'? Is there a more appropriate adjective than 'difficult'?}\EDJreply{Don't you find difficult? At first sight, I cannot understand why this sentence, proposed by Sterling in two of his paper, can be valid mathematically. It only makes sense to me until I am in a type-theoretic world (by Kaposi, since Eq is an inductive type now) (or maybe topos-theoretically where categorical logic will encode equality using data like equalizer). What about changing the phrase to "eccentric" or "weird"?}
A proposition is encoded as a sub\-singleton. For
example, $\setc{\star^1}{\text{ when } t \equiv \true} \uplus \setc{\star^2}{\text{ when } t \equiv \false}$ represents a disjoint union of two
sub\-singleton sets, where the first one is either a singleton if we have a proof of
$t \equiv \true $ or an empty set otherwise.
In other words,
$\star^1$ witnesses a proof that $t \equiv \true$.
Here, $\star$, $\star^1$, $\star^2$ are just some arbitrary fixed elements.
